Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-03-30 chSiGaps/AO_bondedSi.tex
Si Gaps chapter not compiling, possibly due to \ref and \label duplication
fix over-sized figures in the applied optics chapter

\section{Si$-$Si Fabry P\`{e}rot measurement theory}
\label{secTheory}

@@

\subsection{Predicted transmission spectrum for bonded Si with finite interface gap}
\label{secTheory}
A pair of bonded silicon wafers or pucks with a small gap forms three coupled cavities with the air gap as the the central cavity.  The outer cavities, those within the Si, however, were not produced with coherence in mind.  Their sides are not necessarily flat and parallel to the required level and the specifics of their deviation from perfect etalons are usually not known to the level necessary to treat them as coherent structures in the analysis.  The multiple internal reflections within the Si therefore present a hurdle to an analysis of the air gaps.  In the air gap, however, the gap size is small enough that the cavity it forms can always be treated as a coherent structure.  Treatments for multiple coherent reflections have been described in detail in the optics literature \cite{2007fuph.book.....S}.  The wave transfer matrix technique treats each dielectric interface as a matrix with elements relating the pre- and post- interface complex amplitudes in the left and right directions.  We adapted the wave transfer technique for incoherent interactions \cite{2002ApOpt..41.3978K} to deal with the cavities within the thick Si substrates.  Specifically we constructed an incoherent wave transfer matrix whose elements relate the intensities (and not complex amplitudes) before and after an interface.  The details appear in Appendix \ref{sec:Append-IMRTMM}.  We computed the transmission for two scenarios: first a double side polished (DSP) Si sample with no gap, and second a pair of bonded Si samples with a gap thickness $d$.  The DSP Si sample with no air gap has a transmission equal to:

@@

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG03 hole region]{\label{figVG03_corner}}
    	\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_corner.pdf} \newline
    \subfloat[Measured spectrum and fit of VG03 hole region]{\label{figVG03_f100}}
    	\includegraphics[width=\textwidth]{chSiGaps/figs/VG03_f100.pdf}
	\caption{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. See the text for details on the sample, setup, and analysis.  The measured spectrum is the black stepped line.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model.  Wavelengths short-ward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.}
	\label{figVG03full} 
\end{figure}

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG03 petal region]{\label{figVG03p2_corner}}
    	\includegraphics[width=\textwidth]{chSiGaps/figs/VG03p2_corner.pdf} \newline
    \subfloat[Measured spectrum and fit of VG03 petal region]{\label{figVG03_f045}}
    	\includegraphics[width=\textwidth]{chSiGaps/figs/VG03_f045.pdf}
	\caption{ Same as Figure \ref{figVG03full}, but the measurement was in a region where $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued fringes. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. }
	\label{figVG03part}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[Illustration of VG09-12 sample transport accessory measurement positions.]{\label{figVG0912_STA_illus}}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG09_12_STA_illustration.pdf}
    \subfloat[Measured gap transmission spectra of VG09-12 on- and off- mesh ]{\label{figVG0912}}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG0912_STA_scan_coarse.pdf}
	\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.}
	\label{figVG12}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh]{\label{VG0912_0gap_corner}}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG0912_0gap_corner.pdf}
    \subfloat[Measured spectrum of VG09-12]{\label{VG0912_0gap}}
        \includegraphics[width=\textwidth]{chSiGaps/figs/VG0912_0gap.pdf}
	\caption{Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.
	\label{figVG12}}
\end{figure}

>>>>

\section{Si$-$Si Fabry P\`{e}rot measurement theory}

@@

\subsection{Predicted transmission spectrum for bonded Si with finite interface gap}
A pair of bonded silicon wafers or pucks with a small gap forms three coupled cavities with the air gap as the the central cavity.  The outer cavities, those within the Si, however, were not produced with coherence in mind.  Their sides are not necessarily flat and parallel to the required level and the specifics of their deviation from perfect etalons are usually not known to the level necessary to treat them as coherent structures in the analysis.  The multiple internal reflections within the Si therefore present a hurdle to an analysis of the air gaps.  In the air gap, however, the gap size is small enough that the cavity it forms can always be treated as a coherent structure.  Treatments for multiple coherent reflections have been described in detail in the optics literature \cite{2007fuph.book.....S}.  The wave transfer matrix technique treats each dielectric interface as a matrix with elements relating the pre- and post- interface complex amplitudes in the left and right directions.  We adapted the wave transfer technique for incoherent interactions \cite{2002ApOpt..41.3978K} to deal with the cavities within the thick Si substrates.  Specifically we constructed an incoherent wave transfer matrix whose elements relate the intensities (and not complex amplitudes) before and after an interface.  The details appear in Appendix \ref{sec:Append-IMRTMM}.  We computed the transmission for two scenarios: first a double side polished (DSP) Si sample with no gap, and second a pair of bonded Si samples with a gap thickness $d$.  The DSP Si sample with no air gap has a transmission equal to:

@@

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG03 hole region]{\label{figVG03_corner}}
    	\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_corner.pdf} \newline
    \subfloat[Measured spectrum and fit of VG03 hole region]{\label{figVG03_f100}}
    	\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_f100.pdf}
	\caption{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. See the text for details on the sample, setup, and analysis.  The measured spectrum is the black stepped line.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model.  Wavelengths short-ward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.}
	\label{figVG03full} 
\end{figure}

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG03 petal region]{\label{figVG03p2_corner}}
    	\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03p2_corner.pdf} \newline
    \subfloat[Measured spectrum and fit of VG03 petal region]{\label{figVG03_f045}}
    	\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_f045.pdf}
	\caption{ Same as Figure \ref{figVG03full}, but the measurement was in a region where $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued fringes. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. }
	\label{figVG03part}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[Illustration of VG09-12 sample transport accessory measurement positions.]{\label{figVG0912_STA_illus}}
        \includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG09_12_STA_illustration.pdf}
    \subfloat[Measured gap transmission spectra of VG09-12 on- and off- mesh ]{\label{figVG0912}}
        \includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG0912_STA_scan_coarse.pdf}
	\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.}
	\label{figVG12}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh]{\label{VG0912_0gap_corner}}
        \includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG0912_0gap_corner.pdf}
    \subfloat[Measured spectrum of VG09-12]{\label{VG0912_0gap}}
        \includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG0912_0gap.pdf}
	\caption{Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.
	\label{figVG12-STA}}
\end{figure}
